---
title: "notebook20190108"
author: "Mark Hagemann"
date: "January 8, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Since optimizations are going very slow, I thought I'd try out microbenchmark on the objective and gradient. 

```{r}
library(microbenchmark)

foo <- mcflo_inps(swotlist = reachdata$SacramentoUpstream, fl = "metroman", 
                  mc = "metroman", metric = "nrmse")

f1 <- foo$f
g1 <- foo$g
args <- foo$p_init


microbenchmark(f1(args), g1(args))

```


Right, what I really want to do is [profile](http://adv-r.had.co.nz/Profiling.html) my code. I'll use [profvis](https://rstudio.github.io/profvis/) for this.

```{r}
install.packages("profvis")
library(profvis)

p <- profvis( {
    fres <- f1(args)
  print(fres)
})

p
```

That's really cool! Starts off with a total time of 1600 ms. Clearly shows a redundant mcflfun call, and nested within that, 3 redundant flfun calls. Easy to fix! Try now (after some very minor tweaks):

```{r}
foo2 <- mcflo_inps(swotlist = reachdata$SacramentoUpstream, fl = "metroman", 
                  mc = "metroman", metric = "nrmse")

f2 <- foo2$f
g2 <- foo2$g
args <- foo2$p_init

p2 <- profvis( {
  fres <- f2(args)
  print(fres)
})

p2
```


That helped, but it only cut the time in half. Redundancies persist.Try memoising!

```{r}
library(memoise)
```

Now that I've memoised, try a third time.

```{r}
foo3 <- mcflo_inps(swotlist = reachdata$SacramentoUpstream, fl = "metroman", 
                  mc = "metroman", metric = "nrmse")

f3 <- foo3$f
g3 <- foo3$g
args <- foo3$p_init

p3 <- profvis( {
  fres <- f3(args)
  print(fres)
})

p3
```


