  ---
title: "notebook20190118"
author: "Mark Hagemann"
date: "January 18, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I just finished recreating result plots including partial optimization, and the MetroMan results are weird! I need a way to plot logn vs log(A/W) with both closure (points) and MetroMan modeled n (lines) for a given:

1. case (swotlist)
2. A0 vector --> A  matrix (creates closure)
3. a, b vectors (creates MetroMan modeled n)

Relevant info is stored in: reachdata (1, 2)

Can I use mc(fl())(params)?

- Gives a swotlist including Ahat
- params will include a, b
- Looks good, give it a shot.

```{r}
testmcfl <- mc(fl(reachdata$Ganges, method = "metroman", 
                  real_A = TRUE, gradient = FALSE), 
               method = "bam", gradient = FALSE)

matrow <- resultMatrix %>% 
  filter(case == "Ganges", fl == "metroman", mc == "bam", 
         method == "part_optim", metric == "nrmse")

testpars <- resultList[[matrow$msg]]$params

testres <- testmcfl(testpars)

plot_DAWG(testres$Ahat - testres$A)

testclos <- with(testres, 5/3 * log(Ahat) + 1/2 * log(S) - 2/3 * log(W) - log(Q))

testlogd <- with(testres, log(Ahat) - log(W))

plot_DAWG(testclos)

ndplotdf <- swot_tidy(list(logn = testclos, logd = testlogd)) %>% 
  mutate(loc = as.factor(loc))

abdf <- data.frame(parname = names(testpars),
                   parval = unname(testpars),
                   stringsAsFactors = FALSE) %>% 
  mutate(param = splitPiece(parname, "_", 1),
         loc = splitPiece(parname, "_", 2)) %>% 
  select(-parname) %>% 
  spread(key = param, value = parval)

ndplotdf <- swot_tidy(list(logn = testclos, logd = testlogd)) %>% 
  mutate(loc = as.factor(loc)) %>% 
  left_join(abdf, by = "loc") %>% 
  mutate(logn_hat = a + b * logd)

closlist <- swot_untidy(ndplotdf)
plot_DAWG(closlist$logn_hat)

ggplot(ndplotdf, aes(x = logd, y = logn)) + 
  geom_point(aes(group = loc, color = loc)) +
  # geom_abline(aes(group = loc, color = loc, slope = b, intercept = a),
              # data = abdf)
  geom_line(aes(y = logn_hat, group = loc, color = loc))


ggplot() + 
  geom_abline(aes(group = loc, color = loc, slope = b, intercept = a),
              data = abdf) +
  geom_point(aes(x = logd, y = logn, group = loc, color = loc), data = ndplotdf) +
  xlim(0, 20) + ylim(-10, 10)
  
```


Hmmmm... Well I'll have to pick up on this later. 


May be useful to have a "closure" plot alongside, showing points and modeled logn. 


Can I calculate metrics from closure term?

- Not directly, but partly. 

```{r}

# swotlist must have a "Ahat" component
# log_clos is log-transformed closure matrix
qhat_from_clos <- function(swotlist, log_clos) {
  logA <- log(swotlist$Ahat)
  logS <- log(swotlist$S)
  logW <- log(swotlist$W)
  logqhat <- 5/3 * logA + 1/2 * logS - 2/3 * logW - log_clos
  
  logqhat
}

testqhat <- qhat_from_clos(testres, closlist$logn_hat)

plot_DAWG(testqhat)

testmcflo <- metric(mc(fl(reachdata$Ganges, method = "metroman", 
                          real_A = TRUE, gradient = FALSE), 
                      method = "metroman", gradient = FALSE),
                   method = "rrmse", gradient = FALSE)
foo <- testmcfl(testpars)
plot_DAWG(foo$Qhat)
plot_DAWG(foo$Qhat_fl)
plot_DAWG(foo$Qhat_fl) + scale_y_log10()

plot(apply(foo$Qhat_fl, 2, geomMean), type = "l")


testmcflo(testpars)
```

I may have to put some constraint on the optimization.


### Picking up on 1/22

Rather than constrain the optimization, first I should start by working with "omniscient" mc method's pararmeters, and running those through the mcflo. 

- Make sure not to overwrite previous results--they are interesting, and not "incorrect".

- First get a list of mcflo functions.
    - use `mcflo_inps()` as in `master_mcflo`

```{r}

inp_wrapper <- function(case, 
                 fl = c("bam_man", "metroman", "omniscient"), 
                 mc = c("bam", "metroman", "omniscient"), 
                 metric = c("rrmse", "nrmse"), 
                 method = c("stats", "optim", "part_optim"),
                 area = c("unknown", "known"),
                 msg = NA, startparams = NULL,
                 timeout = 600,
                 ...) {

  fl <- match.arg(fl)
  mc <- match.arg(mc)
  metric <- match.arg(metric)
  method <- match.arg(method)
  area <- match.arg(area)
  swotlist <- reachdata[[case]]
  
  optim_inps <- mcflo_inps(swotlist = swotlist, fl = fl, mc = mc, 
                           method = method, metric = metric, msg = msg)
  
  optim_inps
}


funlist <- list()
for (i in 1:nrow(resultMatrix)) {
  # cat(i)
  argrow <- resultMatrix[i, ]
  funlist[[i]] <- with(argrow, inp_wrapper(
    case = case, fl = fl, mc = mc, metric = metric, 
    method = method, msg = msg
  ))$f
}
```

Now I need to make a new resultList, using only the omnisicient parameters. 

```{r}
omnirows <- which(resultMatrix$mc == "omniscient")

# I need a table for matching non-omnisicient parameters to omniscient parameters

omnimat <- resultMatrix %>% 
  filter(mc == "omniscient") %>% 
  mutate(omnirow = msg) %>% 
  select(case:method, -mc, omnirow)

matchmat <- resultMatrix %>% 
  mutate(origrow = msg) %>% 
  select(case:method, origrow) %>% 
  left_join(omnimat)

# Get result from funlist[[origrow]], using parameters from resultList[[omnirow]]

resultList_omni <- list()
for (i in 1:nrow(matchmat)) {
  cat(i, " ")
  origi <- matchmat[i, "origrow"]
  omnii <- matchmat[i, "omnirow"]
  funi <- funlist[[origi]]
  paramsi <- resultList[[omnii]]$params
  resultList_omni[[i]] <- funi(paramsi)
}

resultVec_omni <- unlist(resultList_omni)

summary(resultVec_omni)

```

Get a plot out of this. 

```{r}
plot(resultVec - resultVec_omni)
```


```{r}

plotdata <- resultMatrix %>%
  mutate(result = resultVec_omni)

plotdata %>% 
  ggplot(aes(x = fl, y = result)) + 
  # geom_line() +
  geom_boxplot(aes(fill = mc), outlier.shape = NA) +
  geom_point(aes(fill = mc), 
             shape = 21, alpha = 0.6,
             position = position_jitterdodge(dodge.width = 0.75, 
                                             jitter.width = 0.1)) +
  geom_hline(yintercept = 0.35, linetype = 2) +
  facet_grid(metric ~ method, scales = "free_y") +
  theme_bw() +
  theme(legend.position = "bottom")

# log-transformed version
plotdata %>% 
  filter(result > 1e-9) %>% # for log scale
  ggplot(aes(x = fl, y = result)) + 
  # geom_line() +
  geom_boxplot(aes(fill = mc), outlier.shape = NA) +
  geom_point(aes(fill = mc), 
             shape = 21, alpha = 0.6,
             position = position_jitterdodge(dodge.width = 0.75, 
                                             jitter.width = 0.1)) +
  facet_grid(metric ~ method) +
  theme_bw() +
  scale_y_log10(limits = c(0.001, 1)) +
  annotation_logticks(sides = "l") +
  theme(legend.position = "bottom")
```

Make sure the qhat looks better now.

```{r}
testind_omni <- matchmat$omnirow[which(matchmat$origrow == matrow$msg)]
testpars_omni <- resultList[[testind_omni]]$params


foo_omni <- testmcfl(testpars_omni)
foo <- testmcfl(testpars)

plot_DAWG(foo_omni$Qhat)
plot_DAWG(foo_omni$Qhat_fl)

```

Time to package this up. 

- Make a new src/ script for omniscient mc analysis DONE
- cache relevant objects (possibly renamed) DONE
- Make a new docs/slides deck including the above plots. DONE
- Add a section to src/mcflo-results.Rmd with the above plots. DONE
