---
title: "notebook20181129"
author: "Mark Hagemann"
date: "November 29, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Picking up with optimization from last week. Now (duh) initialize at "statistically correct" parameters. Where did I do this before?

Right, the `manning_peek()` function in lib/optim.R (should move the function).

```{r}

testcase <- reachdata$Ganges %>% 
  # swot_sset(keeplocs = 1, keeptimes = 1:2)
  swot_sset()

statoptim <- manning_peek(testcase)[c("n", "A0")] %>% 
  unlist() %>% 
  log()

ob4 <- mcflob(testcase, mc = "bam", fl = "bam_man", ob = "rrmse")

ob4(statoptim)
numgrad(ob4, statoptim)

## this section for debugging gradient/jacobian
# testcase$Q
# flfun4 <- fl(testcase, "bam_man")
# flfun4(statoptim)$Qhat
# mcflfun4 <- mc_bam(flfun4)
# attr(mcflfun4, "gradient")(statoptim)
# mcflfun4(statoptim)$Qhat

opt4 <- nlm(ob4, p = statoptim)
opt4$minimum
opt4$estimate
statoptim
```

Fixed the BAM mc jacobian! Stupid mistake in chain-law-ing the exponent.

Next: implement MetroMan mass-conservation.

```{r}
testcase <- reachdata$Ganges %>% 
  swot_sset(keeplocs = 1:3, keeptimes = 1:2)
  # swot_sset()
statoptim <- manning_peek(testcase)[c("n", "A0")] %>% 
  unlist() %>% log()

fl5 <- fl(testcase, method = "bam_man")
fl5(statoptim)$Qhat

Ahat <- fl5(statoptim)$Ahat
tmat <- fl5(statoptim)$t
dAdt <- findif_t(Ahat) / findif_t(tmat)
xmat <- fl5(statoptim)$x - mean(fl5(statoptim)$x)
conv <- 1 / (3600 * 24)

Qhat1 <- swot_vec2mat(apply(fl5(statoptim)$Qhat, 2, mean), Ahat)
Qadj <- -dAdt * xmat * conv + mean(dAdt * xmat * conv)
Qhat <- Qhat1 + Qadj

Qhat
testcase$Q

```

That appears to work, but how to do gradient?! May need to simplify.

- Identical to mean if I don't readjust Q (remove mean difference)
- No, appears to be equal to mean even if I center the Qadj (not a function of Qhat). 
- This should be easy.


```{r}
testcase <- reachdata$Ganges %>% 
  swot_sset(keeplocs = 1:3, keeptimes = 1:2)
  # swot_sset()
statoptim <- manning_peek(testcase)[c("n", "A0")] %>% 
  unlist() %>% log()


ob5 <- mcflob(testcase, mc = "bam", fl = "bam_man", ob = "rrmse")

ob5(statoptim)
numgrad(ob5, statoptim)
```

Does it improve on the BAM mass-conservation?

```{r}
testcase <- reachdata$Ganges %>% 
  swot_sset()

statoptim <- manning_peek(testcase)[c("n", "A0")] %>% 
  unlist() %>% 
  log()

ob6 <- mcflob(testcase, mc = "metroman", fl = "bam_man", ob = "rrmse")

ob6(statoptim)
numgrad(ob6, statoptim)

opt6 <- nlm(ob6, p = statoptim)
opt6$minimum
opt6$estimate
statoptim
```

Now I've implemented NRMSE. See how that works.

```{r}
testcase <- reachdata$Ganges %>% 
  swot_sset()

statoptim <- manning_peek(testcase)[c("n", "A0")] %>% 
  unlist() %>% 
  log()

ob7 <- mcflob(testcase, mc = "mean", fl = "bam_man", ob = "nrmse")
# ob7 <- mcflob(testcase, mc = "mean", fl = "bam_man", ob = "rrmse")

ob7(statoptim)
numgrad(ob7, statoptim)

opt7 <- nlm(ob7, p = statoptim)
opt7$minimum
opt7$estimate
statoptim

```

MetroMan now.

```{r}
testcase <- reachdata$Ganges %>% 
  # swot_sset(keeplocs = 1:3, keeptimes = 1:100)
  swot_sset()

statoptim <- manning_peek(testcase, man_n = "metroman")[c("n_a", "n_b", "A0")] %>% 
  within(., {A0 = log(A0)}) %>% 
  unlist() #%>% 
  # log()


ob8 <- mcflob(testcase, mc = "mean", fl = "metroman", ob = "nrmse")
# ob8 <- mcflob(testcase, mc = "mean", fl = "bam_man", ob = "rrmse")

anlyt <- ob8(statoptim)
numer <- numgrad(ob8, statoptim)
summary(attr(anlyt, "gradient") - numer)
attr(anlyt, "gradient")
numer

## this section for debugging gradient/jacobian
# testcase$Q
# flfun4 <- fl(testcase, "bam_man")
# flfun4(statoptim)$Qhat
# mcflfun4 <- mc_bam(flfun4)
# attr(mcflfun4, "gradient")(statoptim)
# mcflfun4(statoptim)$Qhat



opt8 <- nlm(ob8, p = statoptim, print.level = 2)
opt8$minimum
opt8$estimate
statoptim
```

See if deriv can help.

```{r}
expr <- y ~ exp(-a - b * (x + dA) / W) * W^(-2/3) * (x + dA)^(5/3) * S^(1/2)
expr

deriv(expr, c("y", "x"))

```

That's fine. Need to debug manually.

```{r}
testpars <- c(-3.6222916, -3.6063583, -3.5794698, -3.7953999, -1.1410405, 
              -4.0149410, -0.2598782, -0.3232485, -0.4996585, -0.3096474, 
              -1.8025770, -0.1450224, 8.8480024, 9.0065874, 8.6803217, 
               8.8381524, 8.6506848, 8.5974283)
anlyt <- ob8(testpars)
numer <- numgrad(ob8, testpars)
summary(attr(anlyt, "gradient") - numer)
attr(anlyt, "gradient")
numer
```


Now set up the matrix for analysis. 

```{r}
cases <- names(reachdata)
flow_laws <- c("bam_man", "metroman", "omniscient")
mc_types <- c("bam", "metroman", "omniscient")
metrics <- c("rrmse", "nrmse")
methods <- c("stats", "optim")

expand.grid(cases, flow_laws, mc_types, metrics, methods)
```


And a function that takes these columns' values as args. Returns a list with: 

- metric value
- parameters
- call
- nlm results (possibly)


```{r}
master_mcflo <- function(case, 
                         fl = c("bam_man", "metroman", "omniscient"), 
                         mc = c("bam", "metroman", "omniscient"), 
                         metric = c("rrmse", "nrmse"), 
                         method = c("stats", "optim")) {
  fl <- match.arg(fl)
  mc <- match.arg(mc)
  metric <- match.arg(metric)
  method <- match.arg(method)
  swotlist <- reachdata[[case]]
  statparams <- fl_peek(swotlist, fl = fl)
  
  mcflo <- mcflob(swotlist, mc = mc, fl = fl, ob = metric)
  res <- list()
  
  if (fl == "omniscient") {
    res$metric <- mcflo()
    res$params <- numeric()
  } else if (method == "stats") {
    res$metric <- mcflo(statparams)
    res$params <- statparams
  } else if (method == "optim") {
    resopt <- R.utils::withTimeout(nlm(mcflo, p = statparams, iterlim = 500), 
                                   timeout = 3600 * 1.5)
    
    res$metric <- mcflo(resopt$estimate)
    res$params <- resopt$estimate
    res$optim.info <- resopt
  }
  
  res$call <- sys.call()
  res
}

foo <- master_mcflo("Ganges", method = "optim", mc = "omniscient")



```


OK, I need to redo manning_peek

- make it fl_peek
    - have arguments same as fl()
- Return vector of parameters used by fl()()


```{r}
cases <- names(reachdata)
flow_laws <- c("bam_man", "metroman", "omniscient")
mc_types <- c("bam", "metroman", "omniscient")
metrics <- c("rrmse", "nrmse")
methods <- c("stats", "optim")

inputMatrix <- expand.grid(cases, flow_laws, mc_types, metrics, methods, 
                           stringsAsFactors = FALSE, 
                           KEEP.OUT.ATTRS = FALSE) %>% 
  setNames(c("case", "fl", "mc", "metric", "method"))

resultList <- pmap(.l = inputMatrix,
                   .f = possibly(master_mcflo, otherwise = NA))

cache("resultList")
```

See which failed.

```{r}
failures <- is.na(resultList)

inputMatrix$failed <- failures

head(inputMatrix)

inputMatrix %>% 
  group_by(case, method) %>% 
  summarize(pct_fail = sum(failed) / n()) %>% 
  arrange(desc(pct_fail))

inputMatrix %>% 
  group_by(mc, fl, method) %>%
  group_by(metric, method) %>%
  summarize(pct_fail = sum(failed) / n())

```




