---
title: "notebook20181126"
author: "Mark Hagemann"
date: "November 26, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Changing tack a little bit. Still working on mcflo optimization. Now I'll try using nloptr package.

```{r}
install.packages("nloptr")
library(nloptr)
```

For now, just hack the thing to separate the objective from the gradient.


```{r}
testcase <- reachdata$Ganges %>% 
  swot_sset(keeploc = 1:2)
  # swot_sset()
ob1 <- mcflob(swotlist = testcase, 
              mc = "mean", fl = "bam_man")
inits1 <- c(-3.5, bamr::estimate_logA0(testcase$W) + 2)

ob1_f <- ob1
attr(ob1_f, "gradient") <- NULL
ob1_grad <- attr(ob1, "gradient")
```

Using nloptr intro vignette

```{r}
opts1 <- list(algorithm = "NLOPT_LD_LBFGS",
              xto_rel = 1e-8,
              check_derivatives = TRUE)
opt1 <- nloptr(x0 = inits1, eval_f = ob1_f, eval_grad_f = ob1_grad,
               opts = opts1)
opt1$solution
```

Try adding constraints

```{r}
# constraint function
# A_0 >= -median(dA)
# -median(dA) - A_0 <= 0
# -median(dA) - exp(logA0) <= 0

constrfun <- function(params) {
  out <- -apply(testcase$dA, 2, median) - exp(params[-1])
}
constrjac <- function(params) {
  out1 <- diag(-exp(params[-1]))
  out <- cbind(rep(0, nrow(out1)), out1) %*% params
  out
}


opts2 <- list(algorithm = "NLOPT_LD_LBFGS",
              xto_rel = 1e-8,
              check_derivatives = TRUE)
opt2 <- nloptr(x0 = inits1, eval_f = ob1_f, eval_grad_f = ob1_grad,
               eval_g_ineq = constrfun,
               eval_jac_g_eq = constrjac,
               opts = opts1)
opt1$solution
```

It seems like the mcflo is non-convex when A0 is not close to optimum.

- At least for Ganges, bam mc gets to optimum, but mean does not. 


I need to call it a day on this and switch to swot error stuff. 

