---
title: "notebook20181204"
author: "Mark Hagemann"
date: "December 4, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Going for a plot of optimization results. 

- Compare across flow-laws, mass conservation independently.

```{r}
cases <- names(reachdata)
flow_laws <- c("bam_man", "metroman", "omniscient")
mc_types <- c("bam", "metroman", "omniscient")
metrics <- c("rrmse", "nrmse")
methods <- c("stats", "optim")

inputMatrix <- expand.grid(cases, flow_laws, mc_types, metrics, methods, 
                           stringsAsFactors = FALSE, 
                           KEEP.OUT.ATTRS = FALSE) %>% 
  setNames(c("case", "fl", "mc", "metric", "method"))

inputMatrix$result <- resultList %>% 
  map_dbl(possibly(~.$metric, otherwise = NA))
```


```{r}
glimpse(inputMatrix)

inputMatrix %>% 
  filter(metric == "nrmse", fl == "omniscient")

foo <- mcflob(swotlist = reachdata$Connecticut, mc = "bam", fl = "omniscient", ob = "nrmse")
foo()


newresinds <- with(inputMatrix, fl == "omniscient" & metric == "nrmse")
newres <- inputMatrix[newresinds, c("case", "fl", "mc", "metric", "method")] %>% 
  pmap(master_mcflo)

resultList[newresinds] <- newres

inputMatrix$result[newresinds] <- map_dbl(newres, ~.$metric)

```

Now re-cache.

```{r}
summary(inputMatrix)

inputMatrix %>% 
  filter(is.na(result)) %>% 
  group_by(case) %>% 
  summarize(n = n())
  sample_n(20)
  
inputMatrix %>% 
  filter(case == "Cumberland", metric == "nrmse", method == "optim")

foo <- fl_peek(swotlist = reachdata$Cumberland, fl = "bam_man")
foo

swotlist <- reachdata$Cumberland
fl <- "bam_man"
```

Some others don't work because of NA's that geomMean didn't handle (but I fixed it). 

```{r}
newresinds2 <- with(inputMatrix, is.na(result) & method == "stats")
which (newresinds2)

newres2 <- inputMatrix[newresinds2, c("case", "fl", "mc", "metric", "method")] %>% 
  pmap(master_mcflo)

map_dbl(newres2, ~.$metric)


resultList[newresinds2] <- newres2

inputMatrix$result[newresinds2] <- map_dbl(newres2, ~.$metric)
```

Still need to track down others, but forge ahead with results plotting for now.

Key questions:

- How well does each flow law do on its own? 
    - What is the effect of optimizing versus statistical truth?
- How well does each mass-conservation do on its own?
- How well does each combination of mass-conservation and flow law do?

Start with flow laws, mc = "omniscient"

```{r}
inputMatrix %>% 
  filter(mc == "omniscient", fl != "omniscient") %>% 
  glimpse() %>% 
  ggplot(aes(x = method, y = result, group = case)) + 
  geom_point() +
  geom_line() +
  facet_grid(metric ~ fl)
```


Now mass-conservation

```{r}
inputMatrix %>% 
  filter(mc != "omniscient", fl == "omniscient", method == "stats") %>% 
  glimpse() %>% 
  ggplot(aes(x = mc, y = result, group = case)) + 
  geom_point() +
  geom_line() +
  facet_wrap(~metric, nrow = 2)
```

Now how to combine? Separate plots for stats and optim. 

```{r}

plotdata <- inputMatrix %>% 
  filter(mc != "omniscient", fl != "omniscient")

summary(plotdata)

   
ggplot(plotdata, aes(x = fl, y = result)) + 
  # geom_line() +
  geom_boxplot(aes(fill = mc), outlier.shape = NA) +
  geom_point(aes(fill = mc), 
             shape = 21, alpha = 0.6,
             position = position_jitterdodge(dodge.width = 0.75, 
                                             jitter.width = 0.2)) +
  facet_grid(metric ~ method)



```

Next inspect the difference between "optim" and "stats" parameters.

Since many optimized parameters don't come with parameter names, I'll need to put these in ex-post.

```{r}
pnamefun <- function(fl, nparams) {
  if (nparams < 3) return(rep("MISSING", nparams))
  if (fl == "bam_man") {
    ns <- nparams - 1
    pnames <- c("logn", paste0("logA0_", 1:ns))
  } else if (fl == "metroman") {
    ns <- nparams / 3
    pnames <- c(paste0("a_", 1:ns), 
                paste0("b_", 1:ns),
                paste0("logA0_", 1:ns))
  } else {
    pnames <- NULL
  }
  pnames
}
```


```{r}
paramlist <- resultList %>% 
  map(possibly(~.$params, otherwise = c("MISSING" = NA)))

paramlens <- map_int(paramlist, length)

pnamelist <- map2(inputMatrix$fl[paramlens > 0], paramlens[paramlens > 0],
                  pnamefun)

paramdfs_tojoin0 <- paramlist[paramlens > 0] %>% 
  map2(pnamelist, ~data.frame(paramval = .x, 
                              paramname = .y, stringsAsFactors = FALSE))


paramdf_joined <- map2(paramdfs_tojoin0,
                       split(inputMatrix, f = 1:nrow(inputMatrix))[paramlens > 0],
                       ~mutate(.x, fl = .y$fl, mc = .y$mc, method = .y$method,
                               result = .y$result,
                               metric = .y$metric, case = .y$case)) %>% 
  bind_rows()


```

Can I plot it now?

```{r}
paramdf_joined %>% 
  mutate(method = factor(method, levels = c("stats", "optim"))) %>% 
  glimpse() %>% 
  filter(fl %in% c("bam_man", "metroman"),
         metric == "rrmse",
         grepl("logA0", paramname)) %>% 
  ggplot(aes(x = method, y = paramval, color = case, group = paste0(case, paramname))) +
  geom_line(position = position_dodge()) +
  facet_grid(mc ~ fl)

paramdf_joined %>% 
  filter(method == "optim", fl == "metroman", mc == "bam", metric == "rrmse",
         grepl("logA0", paramname),
         case == "MississippiUpstream")


```

Do the same for logn, a, b.

```{r}
paramdf_joined %>% 
  mutate(method = factor(method, levels = c("stats", "optim"))) %>% 
  filter(fl %in% c("bam_man"),
         metric == "rrmse",
         grepl("logn", paramname)) %>% 
  ggplot(aes(x = method, y = paramval, color = case, group = paste0(case, paramname))) +
  geom_line(position = position_dodge()) +
  facet_grid(mc ~ fl)

paramdf_joined %>% 
  mutate(method = factor(method, levels = c("stats", "optim"))) %>% 
  filter(fl %in% c("metroman"),
         metric == "rrmse",
         grepl("^a_", paramname)) %>% 
  ggplot(aes(x = method, y = paramval, color = case, group = paste0(case, paramname))) +
  geom_line(position = position_dodge()) +
  facet_grid(mc ~ fl)

paramdf_joined %>% 
  mutate(method = factor(method, levels = c("stats", "optim"))) %>% 
  filter(fl %in% c("metroman"),
         metric == "rrmse",
         grepl("^b_", paramname)) %>% 
  ggplot(aes(x = method, y = paramval, color = case, group = paste0(case, paramname))) +
  geom_line(position = position_dodge()) +
  facet_grid(mc ~ fl)
```



A curious case is Metroman (flow-law), BAM (mass-conservation) for MississippiUpstream. 

```{r}
paramdf_joined %>% 
  glimpse() %>% 
  filter(fl == "metroman", mc == "bam", case == "MississippiUpstream", metric == "rrmse",
         grepl("logA0", paramname))

whichone <- inputMatrix %>% 
  mutate(thisone = (fl == "metroman" & mc == "bam" & case == "MississippiUpstream" & 
                      metric == "rrmse" & method == "optim")) %>% 
  glimpse()

which(whichone$thisone)
resultList[[which(whichone$thisone)]]

```


This seems like a good place to stop for now. Time for some writing.

```{r}

msus1 <- with(inputMatrix[369, ], 
              master_mcflo(case = case, fl = fl, mc = mc, 
                           metric = metric, method = method))
```


