---
title: "notebook20181204"
author: "Mark Hagemann"
date: "December 4, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Going for a plot of optimization results. 

- Compare across flow-laws, mass conservation independently.

```{r}
cases <- names(reachdata)
flow_laws <- c("bam_man", "metroman", "omniscient")
mc_types <- c("bam", "metroman", "omniscient")
metrics <- c("rrmse", "nrmse")
methods <- c("stats", "optim")

inputMatrix <- expand.grid(cases, flow_laws, mc_types, metrics, methods, 
                           stringsAsFactors = FALSE, 
                           KEEP.OUT.ATTRS = FALSE) %>% 
  setNames(c("case", "fl", "mc", "metric", "method"))

inputMatrix$result <- resultList %>% 
  map_dbl(possibly(~.$metric, otherwise = NA))
```


```{r}
glimpse(inputMatrix)

inputMatrix %>% 
  filter(metric == "nrmse", fl == "omniscient")

foo <- mcflob(swotlist = reachdata$Connecticut, mc = "bam", fl = "omniscient", ob = "nrmse")
foo()


newresinds <- with(inputMatrix, fl == "omniscient" & metric == "nrmse")
newres <- inputMatrix[newresinds, c("case", "fl", "mc", "metric", "method")] %>% 
  pmap(master_mcflo)

resultList[newresinds] <- newres

inputMatrix$result[newresinds] <- map_dbl(newres, ~.$metric)

```

Now re-cache.

```{r}
summary(inputMatrix)

inputMatrix %>% 
  filter(is.na(result)) %>% 
  group_by(case) %>% 
  summarize(n = n())
  sample_n(20)
  
inputMatrix %>% 
  filter(case == "Cumberland", metric == "nrmse", method == "optim")

foo <- fl_peek(swotlist = reachdata$Cumberland, fl = "bam_man")
foo

swotlist <- reachdata$Cumberland
fl <- "bam_man"
```

Some others don't work because of NA's that geomMean didn't handle (but I fixed it). 

```{r}
newresinds2 <- with(inputMatrix, is.na(result) & method == "stats")
which (newresinds2)

newres2 <- inputMatrix[newresinds2, c("case", "fl", "mc", "metric", "method")] %>% 
  pmap(master_mcflo)

map_dbl(newres2, ~.$metric)


resultList[newresinds2] <- newres2

inputMatrix$result[newresinds2] <- map_dbl(newres2, ~.$metric)
```

Still need to track down others, but forge ahead with results plotting for now.

Key questions:

- How well does each flow law do on its own? 
    - What is the effect of optimizing versus statistical truth?
- How well does each mass-conservation do on its own?
- How well does each combination of mass-conservation and flow law do?

Start with flow laws, mc = "omniscient"

```{r}
inputMatrix %>% 
  filter(mc == "omniscient", fl != "omniscient") %>% 
  glimpse() %>% 
  ggplot(aes(x = method, y = result, group = case)) + 
  geom_point() +
  geom_line() +
  facet_grid(metric ~ fl)
```


Now mass-conservation

```{r}
inputMatrix %>% 
  filter(mc != "omniscient", fl == "omniscient", method == "stats") %>% 
  glimpse() %>% 
  ggplot(aes(x = mc, y = result, group = case)) + 
  geom_point() +
  geom_line() +
  facet_wrap(~metric, nrow = 2)
```

Now how to combine? Separate plots for stats and optim. 

```{r}

plotdata <- inputMatrix %>% 
  filter(mc != "omniscient", fl != "omniscient")

summary(plotdata)

   
ggplot(plotdata, aes(x = fl, y = result)) + 
  # geom_line() +
  geom_boxplot(aes(fill = mc)) +
  geom_point(aes(dodge = mc), position = position_jitterdodge(dodge.width = 0.75)) +
  facet_grid(metric ~ method)


```

