---
title: "notebook20181123"
author: "Mark Hagemann"
date: "November 23, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Still trying to get optimization to work. Documenting math in reports/mcflo-math.Rmd.

- I rechecked my math on the Bam-Manning Jacobian. Appears legit (haven't double-checked the vectorization of the matrix)
- Now checking the mass-conservation.
    - Cool, I found a simple bug. Fixed and improved comments.
    
Does it work now? 

```{r}
testcase <- reachdata$Ganges %>% 
  # swot_sset(keeploc = 1)
  swot_sset()
ob1 <- mcflob(swotlist = testcase, 
              mc = "mean", fl = "bam_man")
inits1 <- c(-3.5, bamr::estimate_logA0(testcase$W) + 2)

opt1 <- nlm(ob1, inits1)
opt1$code
opt1$minimum
opt1$iterations
opt1$gradient
attr(ob1, "gradient")(opt1$estimate)
```

Let's make a numerical gradient function to test my work

```{r}
numgrad <- function(fcn, p, delta = 1e-10) {
  val1 <- fcn(p)
  
  toadd <- diag(rep(delta, length(p)))
  newp <- lapply(1:length(p), function(x) p + toadd[, x])
  newvals <- vapply(newp, fcn, numeric(1))
  grad <- (newvals - val1) / delta
  grad
}
```

Test it.

```{r}
numgrad(ob1, inits1)
attr(ob1, "gradient")(inits1)
```

Reveals my gradient is wrong!

Troubleshooting this. Is it the metric_rrmse function? To test that, I need a fake "loaded" mcfl function. 

```{r}

mcflfun <- function(params) {
  set.seed(12493)
  out <- list(Qhat = matrix(params, nrow = 1), 
              Q = matrix(1:6, nrow = 1))
}
attr(mcflfun, "gradient") <- function(params) {
  diag(rep(1, 6))
}
obj2 <- metric_rrmse(mcflfun)

qplot(attr(obj2, "gradient")(0:5), numgrad(obj2, 0:5, delta = 1e-13)) +
  stat_smooth(method = "lm", )
foodf <- data.frame(calc = attr(obj2, "gradient")(0:5),
                    numer = numgrad(obj2, 0:5, delta = 1e-14))
lm(foodf)
```

I think I fixed the rrmse gradient. But Jocobians must still be wrong. Further testing suggests manning jacobian is alright. Must be mass-conservation. 


```{r}
mcfun2 <- structure(
  function (params) {
    set.seed(12493)
    out <- list(Qhat = matrix(params, nrow = 2), Q = matrix(1:6, 
        nrow = 2))
  }, 
  gradient = function (params) {
    diag(rep(1, 6))
  }
)


obj3 <- mc_bam(mcfun2)

obj3(2:7)
diag(attr(obj3, "gradient")(2:7))

```


