---
title: "notebook20181018"
author: "Mark Hagemann"
date: "October 18, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Yesterday I did some work making functions for characterizing Manning from swotlists. Now I should be able to run them all. 

Still need to push on optimization method, but stats method should work. 

```{r}
pep_1n <- reachdata %>% 
  map(~manning_peek(., man_n = "single"))

qhat_1n <- map(pep_1n, ~.$Q)
qreal_1n <- map(reachdata, ~apply(.$Q, 2, geomMean))

rrmse_1n <- map2_dbl(qhat_1n, qreal_1n, ~RRMSE(pred = .x, meas = .y))

plot(rrmse_1n)

```


```{r}
pep_nspa <- reachdata %>% 
  map(~manning_peek(., man_n = "spatial"))

qhat_nspa <- map(pep_nspa, ~.$Q)
qreal_nspa <- map(reachdata, ~apply(.$Q, 2, geomMean))

rrmse_nspa <- map2_dbl(qhat_nspa, qreal_nspa, ~RRMSE(pred = .x, meas = .y))

plot(rrmse_nspa)

plot(rrmse_nspa, rrmse_1n)
all.equal(rrmse_nspa, rrmse_1n)
all.equal(qhat_1n, qhat_nspa)
```

This is the same, and I think it's by definition, since we're aggregating by geomMean for both n and Q. Let's work out a quick proof. 

$$
\begin{aligned}
\log q_t &= \frac{1}{N_s} \sum_s \log\Big(\frac{\dot{q}_{st}}{n_{s}}\Big) \\
&= \frac{1}{N_s} \sum_s (\log \dot{q}_{st} - \log n_{s})\\
&= \frac{1}{N_s} \Big( \sum_s (\log \dot{q}_{st}) - \overline{\log n} \Big)\\
&= \frac{1}{N_s} \Big( \sum_s (\log \dot{q}_{st}) - \overline{\log n} \Big)\\
\end{aligned}
$$

Therefore the geometric mean predicted flow is the same for constant or time-variable Manning n. 


```{r}
pep_nmm <- reachdata %>% 
  map(~manning_peek(., man_n = "metroman"))

qhat_nmm <- map(pep_nmm, ~.$Q)
qreal_nmm <- map(reachdata, ~apply(.$Q, 2, geomMean))


rrmse_nmm <- map2_dbl(qhat_nmm, qreal_nmm, ~RRMSE(pred = .x, meas = .y))

plot(rrmse_nmm)

plot(rrmse_nmm, rrmse_1n); abline(0, 1)
all.equal(rrmse_nmm, rrmse_1n)
all.equal(qhat_1n, qhat_nmm)
```


I'm satisfied with that. Now what can I accomplish with optimization?

```{r}
# Function factories for optimizing based on various fit stats

#' @param evalfun A function returning an evaluation metric to be minimized. 
#'   Must be a function of (pred, meas). 
evalff <- function(swotlist, evalfun = RRMSE,
                  area = c("optim", "stat", "true"), 
                  man_n = c("single", "spatial", "metroman"),
                  qagfun = geomMean) {
  
  area <- match.arg(area)
  man_n <- match.arg(man_n)
  swotlist$dA <- rezero_dA(swotlist$dA, "median")
  
  # params is a vector of length nx + 1, with the first element 
  Qmeas <- apply(swotlist$Q, 2, qagfun)
  
  out <- function(params) {
    stopifnot(is.numeric(params))
    
    if (man_n == "single") {
      n100 <- params[1]
      n <- n100 / 100 # This scaling to keep param on par with A0
      n_n <- 1
      nmat <- matrix(n, nrow = nrow(swotlist$W), ncol = ncol(swotlist$W))
    } else if (man_n == "spatial") {
      n_n <- nrow(swotlist$W)
      n100 <- params[1:n_n]
      n <- n100 / 100
      nmat <- swot_vec2mat(n, swotlist$W)
    } else if (man_n == "metroman") {
      # log(n) = a + b * log(d) = a + b * log(A / W)
      nx <- nrow(swotlist$W)
      logd <- log(swotlist$A) - log(swotlist$W)
      a <- params[1:nx]
      b <- params[nx + (1:nx)]
      nmat <- exp(a + b * logd)
    }
    
    if (area == "optim") {
      A0.001 <- params[-1:-n_n]
      A0 <- A0.001 * 1000 # Scale to keep on par with n.
      dA <- swotlist[["dA"]]
      Amat <- swot_vec2mat(A0, dA) + dA
    } else if (area == "stat") {
      A0 <- apply(swotlist$A, 1, median, na.rm = TRUE)
      dA <- swotlist[["dA"]]
      Amat <- swot_vec2mat(A0, dA) + dA
    } else if (area == "true") {
      Amat <- swotlist[["A"]]
    }
    
    Qpredmat <- nmat^(-1) * Amat^(5/3) * swotlist$W^(-2/3) * swotlist$S^(1/2)
    Qpred <- apply(Qpredmat, 2, qagfun)
    
    out <- evalfun(Qpred, Qmeas)
    out
  }
}

ffs_1n <- map(reachdata, ~evalff(., man_n = "single"))

startn <- lapply(seq_along(ffs_1n), function(x) 0.005)
initA0 <- function(swotlist) {
  exp(bamr:::estimate_logA0(swotlist$W)) * 2
}
startA0 <- map(reachdata, ~initA0(.))

startpars <- map2(startn, startA0, ~c(.x * 100, .y / 1000))

foo <- suppressWarnings(nlm(f = ffs_1n[[1]], p = startpars[[1]], iterlim = 500))

alloptim <- map2(ffs_1n, startpars, 
                 ~suppressWarnings(nlm(.x, p = .y, iterlim = 500)))

allcodes <- map_int(alloptim, ~.$code)
allrrmse <- map_dbl(alloptim, ~.$minimum)

plot(allrrmse)

```

This isn't working, perhaps because n and A0 parameters are such different orders of magnitude. Try with k = 1 / n. And really, more like 50 * k. 

