---
title: "notebook20181112"
author: "Mark Hagemann"
date: "November 12, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Mike made the good point that I should decompose things into flow-law error and mass-conservation error. I have a vague idea of doing this in a functional programming paradigm. For example:

```{r, eval = FALSE}
case <- reachdata$Kanawha
mc(fl(case, method = "manning", params = "optim"), method = "const") # produce a function that returns a swotlist with a Qhat element.
```

Try it out!


```{r}
#' "params" argument is as follows:
#' - "manning_bam": n, then A0_median
#' - "metroman": a (vector), then b vector, then A0_median
fl <- function(swotlist, method = c("manning_bam", "metroman", "amhg"),
               params = "optim") {
  method <- match.arg(method)
  
  W <- swotlist$W
  S <- swotlist$S
  dA <- swotlist$dA
  
  out <- function(params)
  
  if (method == "manning_bam") {
    qdot <- W^{-2/3}
  }
  
}


fl_bam <- function(swotlist) {
  logW <- log(swotlist$W)
  logS <- log(swotlist$S)
  dA <- swotlist$dA
  
  out <- function(params) {
    logn <- params[1]
    A0_med <- params[-1]
    
    logA <- log(swot_A(A0vec = A0_med, dAmat = dA, zero = "median"))
    
    logQ <- -2/3 * logW + 1/2 * logS + 5/3 * logA - logn
    
    outlist <- swotlist
    outlist$Qhat <- exp(logQ)
    return(outlist)
  }
  out
}

mc_bam <- function(swotlist, qpiece = c("choose", "Q", "Qhat")) {
  
  qpiece <- match.arg(qpiece)
  qmat <- get_qmat(swotlist, qpiece)
  
}


mc <- function(swotlist, method = c("bam", "metroman"), 
               qpiece = c("choose", "Q", "Qhat")) {
  qpiece <- match.arg(qpiece)
  
  if (method == "bam") {
    out <- mc_bam(swotlist, qpiece)
  } else if (method == "metroman") {
    out <- mc_mm(swotlist, qpiece)
  }

}

get_qmat <- function(swotlist, qpiece = c("choose", "Q", "Qhat")) {
  qpiece <- match.arg(qpiece)
  if (qpiece == "choose") {
    qpiece <- ifelse(is.null(swotlist[["Qhat"]]), "Q", "Qhat")
  }
  qmat <- swotlist[[qpiece]]
  if (is.null(qmat)) stop(sprintf("%s is missing", qpicece))  
  qmat
}

```


Here is the intended usage. 

```{r, eval = FALSE}
reachdata$Ganges %>% 
  fl("bam_manning") %>% 
  mc("bam") %>% 
  RRMSE(pred = .$Qhat, meas = .$Q)
```

This should be a function of parameters that can be optimized (ideally with a gradient attribute). Also need a function to tidy up the vector of parameters. 

This leaves me with the following analysis matrix. 

- Flow laws
    - omnisciet
    - BAM Manning (constant n)
    - MetroMan (variable n)
    - AMHG
- Mass conservation
    - omniscient
    - MetroMan (dQ/dx = dA/dt)
    - BAM (geometric mean)
    - median
    - mean
- Metrics
    - NRMSE (should be equivalent to linear-space RMSE)
    - RRMSE (should be similar to log-space RMSE)
    - log-space RMSE


## Implementing in lib/mcfl.R

Testing here. 

```{r}
foo <- reachdata$Ganges %>% 
  fl("bam_man")
foo2 <- mc(oper = ., "omniscient")
foo(pinits)
bar <- metric(foo, method = "rrmse")

pinits <- c(-3.5, bamr::estimate_logA0(reachdata$Ganges$W) + 2)

fub <- nlm(bar, pinits)
```

Pipe operator is having some weird functionality here. `mc` is trying to operate on *itself*!

Trying a joined version

```{r}
foo <- reachdata$Ganges %>% 
  mcflob(mc = "bam", fl = "bam_man", ob = "rrmse") %>% 
  nlm(p = pinits)
pbest <- foo$estimate
predfun <- mcfl(reachdata$Ganges, mc = "bam", fl = "bam_man")


bar <- reachdata$Ganges %>% 
  mcflob(mc = "bam", fl = "bam_man", ob = "nrmse") %>% 
  nlm(p = pinits, iterlim = 1500)

foo$estimate
foo$code

```

What I really need are some gradients. 
