---
title: "Methods"
author: "Mark Hagemann"
date: "December 20, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Methods

The best-achievable performance of a discharge algorithm is given by an optimal set of parameters. There are at least two interpretations of this. One uses a physical and statistical interpretation to obtain "true" parameters from SWOT and ancillary data (including true discharge and channel geometry). A second explicitly sets up an optimization problem using a pefrormance meteric calculated from true and predicted discharge. 

This section proceeds by introducing important notation, followed by a description of the benchmark datasets. The two appraoches (physical/statistical and optimization) for obtaining the best flow-law parameters are then presented, with individual variants described in detail. 


### Datasets

```{r, eval = FALSE}
reachdata %>% 
  map_int(~nrow(.$W)) %>%
  summary()

reachdata %>% 
  map_int(~ncol(.$W)) %>%
  summary()
```


19 benchmark datastes used in Durand et al. (2016) were used to characterize algorithm performance. Each dataset is generated using the output from a 2-D hydrodynamic model forced with in-situ channel bathymetry and gaged stage and discharge. The simulation outputs were assembled into reach-averaged "observations" of river width, height, and slope, as well as true cross-sectional area and discharge. The number of locations (reaches) per case varied from 3 to 16, with a median of 5, and the number of times varied from 23 to 367, with a median of 162.

### The components of McFLI discharge algorithms, notation

SWOT discharge algorithms seek to predict discharge in a river using measurements of height, width, and slope. These quantities--including discharge--vary in both space (here indexed by the subscript $s$) and time (indexed by the subscript $t$). Generally, two physical constraints are employed to form the algorithm, although the specifics vary from one algorithm to another. The first is a "flow law", an analytical representation of simplified open-channel hydraulics. The second is mass-conservation within a series of SWOT reaches. The resulting mass-conserved flow law can written as a composition of two functions--a mass-conservation function applied to a flow-law function--as follows:

$$
\hat{Q}_{st} = g_{mcfl}(\theta, \mathbf{x}_{st}) = g_{mc}(g_{fl}(\theta, \mathbf{x}_{st}))
$$

where:

- $\hat{Q}_{st}$ is predicted discharge for location $s$ and time $t$
- $g_{mcfl}$ is the composed mass-conserved flow law function
- $g_{mc}$ is the mass-conservation function
- $g_{fl}$ is the flow-law
- $\theta$ is a vector of flow-law parameters
- $\mathbf{x}_{st}$ is a list of SWOT observations for a particular river case at location $s$ and time $t$. Since $\mathbf{x}$ is fixed for a given dataset, we omit it for simplicity in the the equations below (for example, $g_{fl}(\theta) = g_{fl}(\theta, \mathbf{x}_{st})$)

The performance of a particular discharge algorithm is characterized by a performance metric, which is a function of true and predicted discharge over all $N_s$ locations and $N_t$ times. If $\mathbf{x}$ is augmented to include true discharge (and this information is propogated through the mc and fl functions), then we can write the performance metric for a particular SWOT case, flow law, mass-conservation method, and parameter set, as a further composition:

$$
g^*(\theta) = g_{pm}(g_{mc}(g_{fl}(\theta)))
$$

This general form for mass-conserved flow law performance as a function of parameters and data is readily optimized, providing (1) optimal flow-law parameters for each SWOT case, and (2) best-case performance for a particular mass-conserved flow law, constituting a baseline to which discharge inversion algorithms may be compared. Optimization of equation #### is facilitated by determining its gradient, which is also readily composed from the first derivatives of the individual constituent functions:

$$
\nabla g^*(\theta) = \mathbf{J}_{fl}\mathbf{J}_{mc}\nabla g_{pm}(\theta)
$$

where $\mathbf{J}$ is the Jacobian matrix of the function indicated in the subscript. Specifics of these Jacobians and gradients are provided in the appendix.

Two variants each of flow law, mass-conservation method, and performance metric are described in detail below, representing methods previously applied to the benchmark cases as inversions with documented performance. A third "omniscient" variant of flow law and mass conservation is added as a trivial case in order to parse out the contribution of flow-law and mass-conservation error to overall algorithm performance.

### Flow laws

Manning's equation provides the mathematical basis for most of the proposed SWOT discharge estimation methods, including the two variants considered here. This formula calculates discharge (Q) using measurements of river cross-sectional area (A), slope (S), and width (W). It further has a single unmeasured parameter (n), related to stream bed roughness, that quantifies resistance to flow. 

$$
Q = \frac{1}{n}W^{-2/3}A^{5/3}S^{1/2}
$$

In order to be applied to SWOT measurements, several modifications need to be made. First, because only changes in A are measured (calculated from height and width measurements), and not A itself, the equation receives an additional parameter (A_0), representing the true cross-sectional area at any single point in time. The measured changes in A are denoted $\delta A$, so that $A = A_0 + \delta A$. The SWOT-modified Manning's equation then becomes 

$$
Q = \frac{1}{n}W^{-2/3}(A_0 + \delta A)^{5/3}S^{1/2}
$$

Two specific variants of the SWOT-modified Manning equation are discussed below, as well as a trivial "omniscient" flow law applicable only for testing purposes. Jacobian matrices for these flow laws are described in the appendix.


#### Omniscient (baseline case)

A strictly hypothetical "omniscient" flow law simply returns the true discharge. This function has no parameters. The function has the form:

$$
\hat{Q}_{st} = Q_{st}
$$

where $Q$ (without the hat) represents true discharge.

#### Manning (constant n)

The constant-n Manning equation uses the same value of $n$ across all locations and times. It has the following form:

$$
\hat{Q}_{st} = \frac{1}{n}W_{st}^{-2/3}(A_{0,s} + \delta A_{st})^{5/3}S_{st}^{1/2}
$$

- Manning parameters are $A_{0,s}, s = 1, \dots , N_s$ and $n$
- For numerical stability in optimizing, it is preferable to use $\log A_{0,s}$ and $\log n$. 

#### MetroMan, depth-varying flow resistance

The depth-variable Manning equation is more complex, as it allows $n$ to vary in space and time, according to a location-specific power-law relationship with river depth (calculated as the ratio of cross-sectoinal area to width). This flow law has the following form:

$$
\hat{Q}_{st} = \frac{1}{n_{st}}W_{st}^{-2/3}(A_{0,s} + \delta A_{st})^{5/3}S_{st}^{1/2}, \\
\log n_{st} = a + b \log (A_{st} / W_{st})
$$

- Manning parameters are $\log A_{0,s}, s = 1, \dots , N_s$, $a$, and $b$.

### Mass conservation
 
We shall use a tilde ($\tilde{Q}$) to distinguish mass-conserved discharge estimates from flow-law-only estimates (prior to mass conservation), which are denoted by the hat ($\hat{Q}$).

#### Omnisicent (baseline case)

Similar to the omniscient flow law, the omniscient mass conservation simply returns the flow-law predicted discharge without modification.

$$
\tilde{Q}_{st} = \hat{Q}_{st}
$$

The Jacobian for the omniscient mass-conservation is simply the identity matrix, with dimensions given by the number of parameters used by the flow law.

#### Mean

$$
\tilde{Q}_{st} = \tilde{Q}_t = \frac{1}{N_s}\sum_{s'=1}^{N_s} \hat{Q}_{s't}
$$

#### BAM (geometric mean)

$$
\tilde{Q}_{st} = \tilde{Q}_t = \exp(\frac{1}{N_s}\sum_{s'=1}^{N_s}\log \hat{Q}_{s't})
$$


#### MetroMan (non-steady-state Q)

The MetroMan method of mass-conservation amounts to an adjustment of steady-state Q using information from (estimated) cross-sectional area. This adjustment comes from the instantaneous continuity relationship:

$$
\frac{\partial Q}{\partial x} = -\frac{\partial A}{\partial t}
$$

With sufficient temporal resolution, we can approximate this using a finite difference on an estimate of $A$:

$$
\Delta Q = \frac{\Delta \hat{A}}{\Delta t} \Delta x
$$

where $\hat{A}_{st} = \hat{A}_{0,s} + \delta A_{st}$ and $\Delta x$ is the cumulative along-stream distance between reaches (i.e. the downstream distance of a reach referenced to a single point), with the $\Delta x = 0$ location chosen such that the mean of $\Delta Q$ is zero. 

The total mass-conserved discharge estimate is then

$$
\tilde{Q}_{st} = \tilde{Q}^*_{st} + \Delta Q_{st}
$$

where $\tilde{Q}^*_{st}$ is the steady-state mass-conserved discharge estimate, using the mean method described above. 


### Performanc metric

Two commnoly used performance metrics, both variants of root-mean-square error (RMSE) are considered here: relative RMSE (rRMSE) and normalized RMSE (nRMSE). 

#### rRMSE

$$
\begin{aligned}
rRMSE(\tilde{Q}, Q) &= \sqrt{ \frac{1}{N_s N_{t}} \sum_{s,t} \Bigg( \frac{\tilde{Q}_{st} - Q_{st}}{Q_{st}} \Bigg)^2} \\
&= \Big(\frac{\mathbf{r_r^T r_r}}{N_sN_t}\Big)^{1/2}
\end{aligned}
$$

where $\mathbf{r_r}$ denotes the length-$N_s N_t$ vector of relative residuals. 

#### nRMSE

$$
\begin{aligned}
nRMSE(\tilde{Q}, Q) &= \frac{1}{\bar{Q}}\sqrt{ \frac{1}{N_s N_{t}} \sum_{s,t} (\tilde{Q}_{st} - Q_{st})^2 } \\
&= \frac{1}{\bar{Q}} \Big(\frac{\mathbf{r^T r}}{N_sN_t}\Big)^{1/2}
\end{aligned}
$$

where $\mathbf{r}$ denotes the length-$N_s N_t$ vector of residuals, and $\bar{Q}$ is the arithmetic mean (over all $s$ and $t$) of true discharge. 

### Statistical (non-optimization) approach

While the parameters selected by the optimization described above are optimal in that they minimize the performance metric, they are not necessarily the "truest" parameters. A second approach using physical and statistical interpretations of parameters was therefore used for comparison to the optimization approach. 

True $A_0$ is computed from the true cross-sectional area for each location as the minimum of each location's time series of cross-sectional area:

$$
A_{0, s} = \min_t A_{st}
$$

Assuming no error in approximating $\delta A$ from $H$ and $W$ (which is the case for the synthetic benchmark cases), this is a "true" value of $A_0$ in that $A_{0,s} + \delta A_{st} = A_{st}$

Manning's n is computed from the "closure" term obtained from solving Manning's equation for n using true discharge and cross-sectional area:

$$
n_{st} = Q_{st}^{\space} W_{st}^{2/3}A_{st}^{-5/3}S_{st}^{-1/2}
$$

Constant-n Manning takes the geometric mean of $n_st$ over space and time as the statistically true parameter, while depth-variable (MetroMan) Manning performs a least-squares regression to obtain $a$ and $b$ in the equation $\log n_{st} = a + b \log (A_{st} / W_{st})$.

