---
title: "Results"
author: "Mark Hagemann"
date: "December 21, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

What is the overall idea--do McFl methods work, as evaluated by performance metrics?

- summary statistics: max, median, min RRMSE, NRMSE for non-omniscient methods (4 mcfl methods x 2 metrics)

```{r}
resultMatrix %>% 
  group_by(metric, method) %>% 
  filter(mc != "omniscient", fl != "omniscient") %>% 
  summarize_at(.vars = "result", .funs = funs(median, max), na.rm = TRUE)
```


Is either one or the other responsible for poor McFLI performance? 

Evaluation of individual fl methods

- summary stats for omniscient flow law

Evaluation of individual mc methods

- summary stats for omniscient mass cons.

Comment on differences between metrics

Convergence issues

- Cases, metrics that failed to converge
- diagnostics, interpretation

Relative performance of "stats" method

- Differences in optimal parameters
- interpretation of "truth"

Unresolved questions

Summarize

