---
title: "mcflo-results"
author: "Mark Hagemann"
date: "December 20, 2018"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = TRUE)
opts_knit$set(root.dir = "../")
```

```{r}
library(ProjectTemplate)
load.project()
set.seed(4128)
```


Summary, plots of results from mcflo.R. Copied in part from notebooks 20181129, 20181204.

See which mcflo results failed.

```{r}
resultMatrix %>% 
  group_by(case, method) %>% 
  summarize(pct_fail = sum(failed) / n()) %>% 
  arrange(desc(pct_fail))

resultMatrix %>% 
  group_by(mc, fl, method) %>%
  group_by(metric, method) %>%
  summarize(pct_fail = sum(failed) / n())

```

Plot improvement of optimization over stats-based parameters.

```{r}
library(plotly)
gg1 <- resultMatrix %>% 
  na.omit() %>% 
  mutate(method = factor(method, levels = c("stats", "part_optim", "optim"))) %>% 
  ggplot(aes(x = method, y = result, color = fl, linetype = mc)) + 
  geom_line(aes(group = paste0(case, fl, mc), text = case)) + 
  # scale_linetype_discrete(guide = FALSE) +
  facet_wrap(~metric)
  

gg1
# library(plotly)
ggplotly(gg1 + theme(legend.position = "none"), tooltip = c("text", "y"))
```


Key questions:

- How well does each flow law do on its own? 
    - What is the effect of optimizing versus statistical truth?
- How well does each mass-conservation do on its own?
- How well does each combination of mass-conservation and flow law do?

Start with flow laws, mc = "omniscient"


```{r}
resultMatrix %>% 
  filter(mc == "omniscient", fl != "omniscient") %>% 
  glimpse() %>% 
  ggplot(aes(x = method, y = result, group = case)) + 
  geom_point() +
  geom_line() +
  facet_grid(metric ~ fl)
```


Now mass-conservation

```{r}


gg2 <- resultMatrix %>% 
  filter(mc != "omniscient", fl == "omniscient", method == "stats") %>% 
  ggplot(aes(x = mc, y = result, group = case)) + 
  geom_point() +
  geom_line() +
  facet_wrap(~metric, nrow = 2)

gg2

gg2 + scale_y_log10()
```


Now how to combine? Separate plots for stats and optim. 

```{r}

plotdata <- resultMatrix %>%
  filter()
  # filter(mc != "omniscient", fl != "omniscient")


plotdata %>% 
  ggplot(aes(x = fl, y = result)) + 
  # geom_line() +
  geom_boxplot(aes(fill = mc), outlier.shape = NA) +
  geom_point(aes(fill = mc), 
             shape = 21, alpha = 0.6,
             position = position_jitterdodge(dodge.width = 0.75, 
                                             jitter.width = 0.1)) +
  geom_hline(yintercept = 0.35, linetype = 2) +
  facet_grid(metric ~ method, scales = "free_y") +
  theme_bw() +
  theme(legend.position = "bottom")

# log-transformed version
plotdata %>% 
  filter(result > 1e-9) %>% # for log scale
  ggplot(aes(x = fl, y = result)) + 
  # geom_line() +
  geom_boxplot(aes(fill = mc), outlier.shape = NA) +
  geom_point(aes(fill = mc), 
             shape = 21, alpha = 0.6,
             position = position_jitterdodge(dodge.width = 0.75, 
                                             jitter.width = 0.1)) +
  facet_grid(metric ~ method) +
  theme_bw() +
  scale_y_log10(limits = c(0.001, 1)) +
  annotation_logticks(sides = "l") +
  theme(legend.position = "bottom")
```

Version for slides

```{r, fig.width = 6, fig.height = 4, dpi = 300}

mytheme <- theme_bw() + 
  theme(
    plot.background = element_rect(fill = "#a0a0a0"),
    # text = element_text(size = 15)
    )

slideresdf <- plotdata %>% 
  mutate(fl = plyr::mapvalues(fl, from = c("bam_man", "metroman", "omniscient"),
                              to = c("fl:BAM", "fl:Met", "fl:Omni")),
         metric = plyr::mapvalues(metric, 
                                  from = c("nrmse", "rrmse"),
                                  to = c("nRMSE", "rRMSE")),
         mc = plyr::mapvalues(mc, from = c("bam", "metroman", "omniscient"),
                              to = c("mc:BAM", "mc:Met", "mc:Omni")))

slideresdf <- plotdata %>%
  mutate(fl = plyr::mapvalues(fl, from = c("bam_man", "metroman", "omniscient"),
                              to = c("fl:BAM", "fl:Met", "fl:Omni")),
         metric = plyr::mapvalues(metric,
                                  from = c("nrmse", "rrmse"),
                                  to = c("nRMSE", "rRMSE")),
         mc = plyr::mapvalues(mc, from = c("bam", "metroman", "omniscient"),
                              to = c("mc:BAM", "mc:Met", "mc:Omni")))

slideresgg <- ggplot(slideresdf, aes(x = fl, y = result, text = case)) + 
  # geom_line() +
  geom_boxplot(aes(fill = mc, group = paste0(mc, fl)), outlier.shape = NA) +
  geom_point(aes(fill = mc, group = paste0(mc, fl)), 
             shape = 21, alpha = 0.6,
             position = position_jitterdodge(dodge.width = 0.75, 
                                             jitter.width = 0.1)) +
  geom_hline(yintercept = 0.35, linetype = 2) +
  facet_grid(metric ~ method, scales = "free_y") +
  mytheme +
  scale_y_continuous(name = NULL) + 
  scale_x_discrete(name = NULL) +
  scale_fill_discrete(name = NULL) +
  theme(legend.position = "bottom")


slideresgg

ggsave("../graphs/slides/mcflo-res-boxplots.png")

slideresgg_plotly <- slideresgg
slideresgg_plotly$layers <- slideresgg$layers[-1]
pltly1 <- ggplotly(slideresgg_plotly, tooltip = "text")
save(pltly1, file = "../docs/slides/plotly/slideres_plotly.RData")
```

Omnisicent-mc version (slides only)

```{r, fig.width = 6, fig.height = 4, dpi = 300}
slideresdf <- resultMatrix_omni %>% 
  mutate(fl = plyr::mapvalues(fl, from = c("bam_man", "metroman", "omniscient"),
                              to = c("fl:BAM", "fl:Met", "fl:Omni")),
         metric = plyr::mapvalues(metric, 
                                  from = c("nrmse", "rrmse"),
                                  to = c("nRMSE", "rRMSE")),
         mc = plyr::mapvalues(mc, from = c("bam", "metroman", "omniscient"),
                              to = c("mc:BAM", "mc:Met", "mc:Omni")))

slideresdf <- resultMatrix_omni %>%
  mutate(fl = plyr::mapvalues(fl, from = c("bam_man", "metroman", "omniscient"),
                              to = c("fl:BAM", "fl:Met", "fl:Omni")),
         metric = plyr::mapvalues(metric,
                                  from = c("nrmse", "rrmse"),
                                  to = c("nRMSE", "rRMSE")),
         mc = plyr::mapvalues(mc, from = c("bam", "metroman", "omniscient"),
                              to = c("mc:BAM", "mc:Met", "mc:Omni")))

slideresgg <- ggplot(slideresdf, aes(x = fl, y = result, text = case)) + 
  # geom_line() +
  geom_boxplot(aes(fill = mc, group = paste0(mc, fl)), outlier.shape = NA) +
  geom_point(aes(fill = mc, group = paste0(mc, fl)), 
             shape = 21, alpha = 0.6,
             position = position_jitterdodge(dodge.width = 0.75, 
                                             jitter.width = 0.1)) +
  geom_hline(yintercept = 0.35, linetype = 2) +
  facet_grid(metric ~ method, scales = "free_y") +
  mytheme +
  scale_y_continuous(name = NULL) + 
  scale_x_discrete(name = NULL) +
  scale_fill_discrete(name = NULL) +
  theme(legend.position = "bottom")


slideresgg

ggsave("../graphs/slides/mcflo-omni-res-boxplots.png")

slideresgg_plotly <- slideresgg
slideresgg_plotly$layers <- slideresgg$layers[-1]
pltly1 <- ggplotly(slideresgg_plotly, tooltip = "text")
pltly1
save(pltly1, file = "../docs/slides/plotly/slideres_omni_plotly.RData")
```



Table of how many successfully converged

```{r}
plotdata %>% 
  filter(!is.na(result)) %>% 
  group_by(method, metric, mc, fl) %>% 
  summarize(n = n()) %>% 
  arrange(desc(n)) %>% 
  knitr::kable()
```




Next inspect the difference between "optim" and "stats" parameters.

Since many optimized parameters don't come with parameter names, I'll need to put these in ex-post.

```{r}

paramdf_joined <- resultList %>% 
  map(~data.frame(paramname = names(.$params), value = .$params,
                  stringsAsFactors = FALSE)) %>% 
  bind_rows(.id = "listid") %>% 
  mutate(param = splitPiece(paramname, "_", 1),
         listid = as.numeric(listid),
         locid = as.numeric(splitPiece(paramname, "_", 2))) %>% 
  left_join(mutate(resultMatrix, listid = msg), by = "listid") %>% 
  select(paramname, value, param, locid, case, fl, mc, metric, method) %>% 
  spread(key = method, value = value) %>% 
  mutate(part_optim = ifelse(param == "logA0", stats, part_optim)) %>% 
  gather(key = method, value = paramval, -paramname:-metric) %>% 
  mutate(method = factor(method, levels = c("stats", "part_optim", "optim")))

```

Make the plots

```{r}

# logA0
paramdf_joined %>% 
  filter(fl %in% c("bam_man", "metroman"),
         metric == "rrmse",
         grepl("logA0", paramname)) %>% 
  ggplot(aes(x = method, y = paramval)) +
  geom_line(aes(color = case, 
             group = paste0(case, paramname))) +
  geom_violin(fill = NA) +
  facet_grid(mc ~ fl)

# logn
paramdf_joined %>% 
  filter(fl %in% c("bam_man"),
         metric == "rrmse",
         grepl("logn", paramname)) %>% 
  ggplot(aes(x = method, y = paramval, color = case, 
             group = paste0(case, paramname))) +
  geom_line(position = position_dodge()) +
  facet_grid(mc ~ fl)

# MetroMan slope
paramdf_joined %>% 
  filter(fl %in% c("metroman"),
         metric == "rrmse",
         grepl("^a_", paramname)) %>% 
  ggplot(aes(x = method, y = paramval, color = case, 
             group = paste0(case, paramname))) +
  geom_line(position = position_dodge()) +
  facet_grid(mc ~ fl)

# MetroMan intercept
paramdf_joined %>% 
  filter(fl %in% c("metroman"),
         metric == "rrmse",
         grepl("^b_", paramname)) %>% 
  ggplot(aes(x = method, y = paramval, color = case, 
             group = paste0(case, paramname))) +
  geom_line(position = position_dodge()) +
  facet_grid(mc ~ fl)

```


Try combining all these

```{r, fig.width=6, fig.height=7.5}
paramdf_joined %>% 
  mutate(flparam = paste(param, fl, sep = "_")) %>% 
  filter(fl %in% c("bam_man", "metroman"),
         metric == "rrmse", paramname != "MISSING") %>% 
  ggplot(aes(x = method, y = paramval)) +
  geom_line(aes(color = case, 
             group = paste0(case, paramname))) +
  geom_violin(fill = NA) +
  facet_grid(flparam ~ mc, scales = "free") + 
  theme(legend.position = "right")
```

Pared down version for slides. 

```{r, fig.width = 6, fig.height = 4, dpi = 300}
slidepardf <- paramdf_joined %>% 
  mutate(fl = plyr::mapvalues(fl, from = c("bam_man", "metroman", "omniscient"),
                              to = c("fl:BAM", "fl:Met", "fl:Omni")),
         mc = plyr::mapvalues(mc, from = c("bam", "metroman", "omniscient"),
                              to = c("mc:BAM", "mc:Met", "mc:Omni")),
         flparam = paste(fl, param, sep = "_")) %>% 
  # summary()
  filter(fl %in% c("fl:BAM", "fl:Met"),
         !grepl("^logA0", paramname),
         metric == "rrmse", paramname != "MISSING")

slidepargg <- ggplot(slidepardf, aes(x = method, y = paramval)) +
  geom_line(aes(color = case, 
             group = paste0(case, paramname))) +
  geom_point(aes(color = case)) +
  geom_violin(fill = NA) +
  facet_grid(flparam ~ mc, scales = "free") + 
  scale_y_continuous(name = NULL) +
  scale_x_discrete(name = NULL) +
  mytheme +
  theme(legend.position = "none")
slidepargg
ggsave("graphs/slides/mcflo-param-lineplots.png")

pltly2 <- ggplotly(slidepargg)
save(pltly2, file = "docs/slides/plotly/slidepars_plotly.RData")
```


```{r, fig.width = 6, fig.height = 4, dpi = 300}
paramdf_joined %>% 
  mutate(fl = plyr::mapvalues(fl, from = c("bam_man", "metroman", "omniscient"),
                              to = c("fl:BAM", "fl:Met", "fl:Omni")),
         mc = plyr::mapvalues(mc, from = c("bam", "metroman", "omniscient"),
                              to = c("mc:BAM", "mc:Met", "mc:Omni")),
         flparam = paste(fl, param, sep = "_"),
         paramval = exp(paramval)) %>% 
  # summary()
  filter(fl %in% c("fl:BAM", "fl:Met"),
         grepl("^logA0", paramname),
         metric == "rrmse", paramname != "MISSING") %>% 
  ggplot(aes(x = method, y = paramval)) +
  geom_line(aes(color = case, 
             group = paste0(case, paramname))) +
  geom_point(aes(color = case)) +
  geom_violin(fill = NA) +
  facet_grid(flparam ~ mc, scales = "free") + 
  # scale_y_continuous(name = NULL) +
  scale_y_log10(name = NULL) +
  scale_x_discrete(name = NULL) +
  annotation_logticks(sides = "l") +
  mytheme +
  theme(legend.position = "none")

ggsave("graphs/slides/mcflo-A0-lineplots.png")

```

Better to compare A0 in relative terms. 

This one shifts in log space:

```{r, fig.width = 6, fig.height = 4, dpi = 300}

sliderelA0df <- paramdf_joined %>% 
  mutate(fl = plyr::mapvalues(fl, from = c("bam_man", "metroman"),#, "omniscient"),
                              to = c("fl:BAM", "fl:Met")), #, "fl:Omni")),
         mc = plyr::mapvalues(mc, from = c("bam", "metroman", "omniscient"),
                              to = c("mc:BAM", "mc:Met", "mc:Omni")),
         flparam = paste(fl, param, sep = "_")) %>% 
  filter(fl %in% c("fl:BAM", "fl:Met"),
         metric == "rrmse",
         grepl("logA0", paramname)) %>%
  spread(key = method, value = paramval) %>% 
  mutate(optim = exp(optim - stats), stats = 1) %>%
  select(case, flparam, optim, stats, mc) %>% 
  gather(key = method, value = rel_pval, -case, -mc, -flparam) %>% 
  mutate(method = factor(method, levels = c("stats", "optim"))) %>% 
  group_by(mc, method, flparam) %>% 
  mutate(linegroup = 1:n())

sliderelA0gg <- ggplot(sliderelA0df, aes(x = method, y = rel_pval)) +
  geom_line(aes(color = case, 
                group = linegroup)) + 
  geom_point(aes(color = case)) + 
  geom_violin(fill = NA) +
  facet_grid(flparam ~ mc) + #, scales = "free") +
  scale_y_log10(name = "A0 relative to truth") + 
  scale_x_discrete(name = NULL) +
  annotation_logticks(sides = "l") +
  mytheme +
  theme(legend.position = "none")

sliderelA0gg
ggsave("graphs/slides/mcflo-relA0-lineplots.png")

pltly3 <- ggplotly(sliderelA0gg)
save(pltly3, file = "docs/slides/plotly/sliderelA0_plotly.RData")
```

This one is an honest relative comparison:

```{r}
# logA0
paramdf_joined %>% 
  mutate(method = factor(method, levels = c("stats", "optim"))) %>% 
  filter(fl %in% c("bam_man", "metroman"),
         metric == "rrmse",
         grepl("logA0", paramname)) %>%
  spread(key = method, value = paramval) %>% 
  mutate(pct_chg = (exp(optim) - exp(stats)) / exp(stats) * 100) %>% 
  # filter(pct_chg < 1000000) %>% 
  # glimpse()
  ggplot(aes(x = case, y = abs(pct_chg), 
             group = paste0(case, paramname))) +
  geom_point() +
  facet_grid(mc ~ fl, scales = "free_y") +
  scale_y_log10() +
  theme(axis.text.x = element_text(angle = 90)) +
  ylab("% difference (abs. val.)")
```

### Why do stats and optim differ so much in so many cases?

I need a dawg-like plot, annotated with different models for Manning n. 

```{r}

case1 <- "Ganges"
fl1 <- "metroman"
mc1 <- "metroman"

matrow <- resultMatrix %>% 
  filter(case == case1, fl == fl1, mc == mc1, metric == "rrmse")

pars1 <- resultList[[matrow$msg[1]]]$params # stats
pars2 <- resultList[[matrow$msg[2]]]$params # optim


fun1 <- mc(fl(swotlist = reachdata[[case1]], method = fl1, gradient = FALSE), 
           method = mc1, gradient = FALSE)

errmat1 <- with(fun1(pars1), log(Q / Qhat))
errmat2 <- with(fun1(pars2), log(Q / Qhat))

```

Hmm, I think I should leave this as a todo for now. Time to come up with some slides for tomorrow. Challenge is to:

- Explain the problem, motivation
- Explain the approach
  - define mcflo, components
  - Show matrix of analyses
- Show results


