---
title: "mcflo-results"
author: "Mark Hagemann"
date: "December 20, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Summary, plots of results from mcflo.R. Copied in part from notebooks 20181129, 20181204.

See which mcflo results failed.

```{r}
resultMatrix %>% 
  group_by(case, method) %>% 
  summarize(pct_fail = sum(failed) / n()) %>% 
  arrange(desc(pct_fail))

resultMatrix %>% 
  group_by(mc, fl, method) %>%
  group_by(metric, method) %>%
  summarize(pct_fail = sum(failed) / n())

```

Plot improvement of optimization over stats-based parameters.

```{r}
library(plotly)
gg1 <- resultMatrix %>% 
  na.omit() %>% 
  mutate(method = factor(method, levels = c("stats", "optim"))) %>% 
  ggplot(aes(x = method, y = result, color = fl, linetype = mc)) + 
  geom_line(aes(group = paste0(case, fl, mc), text = case)) + 
  # scale_linetype_discrete(guide = FALSE) +
  facet_wrap(~metric)
  

gg1
# library(plotly)
ggplotly(gg1 + theme(legend.position = "none"), tooltip = c("text", "y"))
```


Key questions:

- How well does each flow law do on its own? 
    - What is the effect of optimizing versus statistical truth?
- How well does each mass-conservation do on its own?
- How well does each combination of mass-conservation and flow law do?

Start with flow laws, mc = "omniscient"


```{r}
resultMatrix %>% 
  filter(mc == "omniscient", fl != "omniscient") %>% 
  glimpse() %>% 
  ggplot(aes(x = method, y = result, group = case)) + 
  geom_point() +
  geom_line() +
  facet_grid(metric ~ fl)
```


Now mass-conservation

```{r}
resultMatrix %>% 
  filter(mc != "omniscient", fl == "omniscient", method == "stats") %>% 
  glimpse() %>% 
  ggplot(aes(x = mc, y = result, group = case)) + 
  geom_point() +
  geom_line() +
  facet_wrap(~metric, nrow = 2)
```


Now how to combine? Separate plots for stats and optim. 

```{r}

plotdata <- resultMatrix %>%
  filter()
  # filter(mc != "omniscient", fl != "omniscient")

plotdata %>% 
  ggplot(aes(x = fl, y = result)) + 
  # geom_line() +
  geom_boxplot(aes(fill = mc), outlier.shape = NA) +
  geom_point(aes(fill = mc), 
             shape = 21, alpha = 0.6,
             position = position_jitterdodge(dodge.width = 0.75, 
                                             jitter.width = 0.1)) +
  facet_grid(metric ~ method) +
  theme_bw() +
  theme(legend.position = "bottom")

# log-transformed version
plotdata %>% 
  filter(result > 1e-9) %>% # for log scale
  ggplot(aes(x = fl, y = result)) + 
  # geom_line() +
  geom_boxplot(aes(fill = mc), outlier.shape = NA) +
  geom_point(aes(fill = mc), 
             shape = 21, alpha = 0.6,
             position = position_jitterdodge(dodge.width = 0.75, 
                                             jitter.width = 0.1)) +
  facet_grid(metric ~ method) +
  theme_bw() +
  scale_y_log10(limits = c(0.001, 1)) +
  annotation_logticks(sides = "l") +
  theme(legend.position = "bottom")
```

Table of how many successfully converged

```{r}
plotdata %>% 
  filter(!is.na(result)) %>% 
  group_by(method, metric, mc, fl) %>% 
  summarize(n = n()) %>% 
  arrange(desc(n)) %>% 
  knitr::kable()
```




Next inspect the difference between "optim" and "stats" parameters.

Since many optimized parameters don't come with parameter names, I'll need to put these in ex-post.

```{r}
pnamefun <- function(fl, nparams) {
  if (nparams < 3) return(rep("MISSING", nparams))
  if (fl == "bam_man") {
    ns <- nparams - 1
    pnames <- c("logn", paste0("logA0_", 1:ns))
  } else if (fl == "metroman") {
    ns <- nparams / 3
    pnames <- c(paste0("a_", 1:ns), 
                paste0("b_", 1:ns),
                paste0("logA0_", 1:ns))
  } else {
    pnames <- NULL
  }
  pnames
}

paramlist <- resultList %>% 
  map(possibly(~.$params, otherwise = c("MISSING" = NA)))

paramlens <- map_int(paramlist, length)

pnamelist <- map2(resultMatrix$fl[paramlens > 0], paramlens[paramlens > 0],
                  pnamefun)

paramdfs_tojoin0 <- paramlist[paramlens > 0] %>% 
  map2(pnamelist, ~data.frame(paramval = .x, 
                              paramname = .y, stringsAsFactors = FALSE))


paramdf_joined <- map2(paramdfs_tojoin0,
                       split(resultMatrix, f = 1:nrow(resultMatrix))[paramlens > 0],
                       ~mutate(.x, fl = .y$fl, mc = .y$mc, method = .y$method,
                               result = .y$result,
                               metric = .y$metric, case = .y$case)) %>% 
  bind_rows()
```

Make the plots

```{r}

# logA0
paramdf_joined %>% 
  mutate(method = factor(method, levels = c("stats", "optim"))) %>% 
  filter(fl %in% c("bam_man", "metroman"),
         metric == "rrmse",
         grepl("logA0", paramname)) %>% 
  ggplot(aes(x = method, y = paramval)) +
  geom_line(aes(color = case, 
             group = paste0(case, paramname))) +
  geom_violin(fill = NA) +
  facet_grid(mc ~ fl)

# logn
paramdf_joined %>% 
  mutate(method = factor(method, levels = c("stats", "optim"))) %>% 
  filter(fl %in% c("bam_man"),
         metric == "rrmse",
         grepl("logn", paramname)) %>% 
  ggplot(aes(x = method, y = paramval, color = case, 
             group = paste0(case, paramname))) +
  geom_line(position = position_dodge()) +
  facet_grid(mc ~ fl)

# MetroMan slope
paramdf_joined %>% 
  mutate(method = factor(method, levels = c("stats", "optim"))) %>% 
  filter(fl %in% c("metroman"),
         metric == "rrmse",
         grepl("^a_", paramname)) %>% 
  ggplot(aes(x = method, y = paramval, color = case, 
             group = paste0(case, paramname))) +
  geom_line(position = position_dodge()) +
  facet_grid(mc ~ fl)

# MetroMan intercept
paramdf_joined %>% 
  mutate(method = factor(method, levels = c("stats", "optim"))) %>% 
  filter(fl %in% c("metroman"),
         metric == "rrmse",
         grepl("^b_", paramname)) %>% 
  ggplot(aes(x = method, y = paramval, color = case, 
             group = paste0(case, paramname))) +
  geom_line(position = position_dodge()) +
  facet_grid(mc ~ fl)

```


Try combining all these

```{r, fig.width=6, fig.height=7.5}
paramdf_joined %>% 
  mutate(method = factor(method, levels = c("stats", "optim")),
         shortparam = markstats::splitPiece(paramname, split = "_", piece = 1),
         flparam = paste(shortparam, fl, sep = "_")) %>% 
  filter(fl %in% c("bam_man", "metroman"),
         metric == "rrmse", paramname != "MISSING") %>% 
  ggplot(aes(x = method, y = paramval)) +
  geom_line(aes(color = case, 
             group = paste0(case, paramname))) +
  geom_violin(fill = NA) +
  facet_grid(flparam ~ mc, scales = "free") + 
  theme(legend.position = "right")

```



Better to compare A0 in relative terms. 

```{r}
# logA0
paramdf_joined %>% 
  mutate(method = factor(method, levels = c("stats", "optim"))) %>% 
  filter(fl %in% c("bam_man", "metroman"),
         metric == "rrmse",
         grepl("logA0", paramname)) %>%
  select(-result) %>% 
  spread(key = method, value = paramval) %>% 
  mutate(pct_chg = (exp(optim) - exp(stats)) / exp(stats) * 100) %>% 
  # filter(pct_chg < 1000000) %>% 
  # glimpse()
  ggplot(aes(x = case, y = abs(pct_chg), 
             group = paste0(case, paramname))) +
  geom_point() +
  facet_grid(mc ~ fl) +
  scale_y_log10() +
  theme(axis.text.x = element_text(angle = 90))
```

